---
title: "Supplementary Figure S3"
author: "Kristine A. Tsantilas, PhD"
date: "08/19/2024"
output: 
  html_document:
      code_folding: hide
      toc: true
      toc_float:
        collapsed: false
---

# Overview

R Markdown to generate a Supplementary Figure examining the overlap of the ExoCarta extracellular vesicle database relative to proteins found in Mag-Net. The code produces Supplementary Figure S3.
 
<br/><br/>


## Experiment

Characterization of Mag-Net enrichment of circulating membrane particles. The same dataset in "Figs_2C_3A_3B_5B__SuppFigs_S1_S5_S6.Rmd" in this repository which was used to generate Figures 2C, 3A, 3B, and Supplementary Figure S2

<br/><br/>


# Data Import and Formatting {.tabset .tabset-fade}

## Input

List of proteins found in exosomes per ExoCarta (ExoCarta_top100_protein_details_5.txt) under "Download" in the ExoCarta Download - 5 (Release date: 29 July 2015), Uniprot accession numbers mapped from genes in the ExoCarta list, and a dataframe output from the script where the protein fold-change data was processed in the R Markdown "Figs_2C_3A_3B_5B__SuppFigs_S1_S5_S6.Rmd" in this repository. The dated output was included in the GitHub **csv** folder.

* EXOCARTA_PROTEIN_MRNA_DETAILS_5_2024_06_18.csv

* EXOCARTA_PROTEIN_MRNA_DETAILS_5_idmapping_2024_06_18.csv

* 2024May31_EnrichDeplet_TIC_FCtype.csv


<br/><br/>


## Output

This R Markdown produces 1 Supplementary Figure as an svg file: 

* ** Figure S2:** Histograms and volcano plots illustrating the overlap of the proteins found in Mag-Net relative to the top 1000 and the top 100 most frequently identified markers in exosomes at the protein-level from the ExoCarta database.

$~$

<br/><br/>


## Software Information

* Skyline Daily (64-bit)

* R version: 4.3.2

* R Studio version: 2023.03.0+386 "Cherry Blossom" Release (3c53477afb13ab959aeb5b34df1f10c237b256c3, 2023-03-09) for Windows
Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) RStudio/2023.03.0+386 Chrome/108.0.5359.179 Electron/22.0.3 Safari/537.36

* Packages required: 

  + dplyr (version 1.1.4)
  
  + stringr (version 1.5.1)
  
  + tidyr (version 1.3.1)
  
  + ggplot2 (version 3.5.0)
  
  + ggrepel (version 0.9.5)

  + knitr (version 1.45)
  
  + kableExtra (version 1.4.0)
  
  + eulerr (version 7.0.2)
  
  + patchwork (version 1.2.0)

* Inkscape: 1.1 (c68e22c387, 2021-05-23)

  
<br/><br/>


```{r package_installation, include=FALSE}

# Download necessary packages for analysis
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(knitr)
library(kableExtra)
library(eulerr)
library(patchwork)

# Check session info
sessionInfo()

```


```{r setup, include=FALSE}
# Set-up current date to include in filename output
(today <- Sys.Date())
basename <- today %>%
            format(., "%Y%b%d") %>% # with month as a word
            paste0(.,"_")

# Set-up base filenames by dataset to classify filename output
exocarta <- "exocarta_"

```


```{r setup_folders}

directories <- c('output', 'output/plots', 'output/tables')

for(c in directories){
  if(!dir.exists(c)){
    message(paste('Creating directory: ', c))
    dir.create(c)
  }}

```


<br/><br/>


## File Import

Importing data from ExoCarta and from Skyline.

* The Protein/mRNA data was downloaded from ExoCarta on June 17, 2024 (ExoCarta Download - 5 (Release date: 29 July 2015)) under the "Download" tab.

* Mag-Net protein-level data was extracted from Skyline's group comparison document grid.

$~$

```{r file_import}
# ExoCarta data
    # Import EV protein/mRNA list downloaded from ExoCarta on June 17, 2024 (ExoCarta Download - 5 (Release date: 29 July 2015))
            ev_mrna_prot <- read.csv("csv\\EXOCARTA_PROTEIN_MRNA_DETAILS_5_2024_06_18.csv", 
                                  header = TRUE,
                                  na.strings="#N/A",
                                  sep = ",")
    
    # Import the table generated in Uniprot containing the top human-only protein's gene names and the protein Accession numbers mapped to the gene names
            id_mapping_human <- read.csv("csv\\EXOCARTA_PROTEIN_MRNA_DETAILS_5_idmapping_2024_06_18.csv",
                                header = TRUE,
                                na.strings="#N/A",
                                sep = ",")

# Mag-Net data
        magnet_input <- read.csv("csv\\2024May31_EnrichDeplet_TIC_FCtype.csv",
                              header = TRUE,
                              na.strings="#N/A",
                              sep = ",")

```


<br/><br/>

## ExoCarta Protein List

The downloaded protein list from ExoCarta was filtered to only include protein entries and those found in humans.

$~$


```{r exocarta_human}

ev_prot_filtered <- ev_mrna_prot %>% 
                    filter(CONTENT.TYPE == "protein") 

ev_prot_human <- ev_prot_filtered %>% 
                 filter(SPECIES == "Homo sapiens") 

# Make all gene names capitalized.
ev_prot_human$GENE.SYMBOL.C <- toupper(ev_prot_human$GENE.SYMBOL)
                 

ev_prot_human_counts <- ev_prot_human %>%
                        group_by(GENE.SYMBOL.C) %>%
                        summarise(unique_experiments = n_distinct(EXPERIMENT.ID)) %>%
                        .[order(.$unique_experiments, decreasing = TRUE),] 


write.csv(ev_prot_human_counts, paste("output//tables//",basename,exocarta,"human_ev_protein_list.csv", sep=""), quote=FALSE, row.names=FALSE)

```

$~$

The downloaded gene IDs in the exported "2024Jun18_exocarta_human_ev_protein_list.csv" were matched to Uniprot Accession numbers using the "Retrieve/ID mapping" tool on _*Uniprot.org*_ and re-imported above as "EXOCARTA_PROTEIN_MRNA_DETAILS_5_idmapping_2024_06_18.csv".

> 5,260 IDs were mapped to 5,409 results
> 146 ID were not mapped

$~$

```{r import_manual_id_mapping}
id_mapping_human_renamed <- id_mapping_human %>%
                            rename("GENE.SYMBOL.C" = "From", 
                                   "Protein.Accession" = "Entry")
ev_human_list_ids <- full_join(ev_prot_human_counts, id_mapping_human_renamed, by = "GENE.SYMBOL.C")

ev_human_list_ids_filtered <- ev_human_list_ids %>%
                              filter(Protein.Accession != "NA")

write.table(ev_human_list_ids_filtered, paste0("output//tables//",basename,exocarta,"human_ev_protein_ids.tsv"), quote=FALSE, row.names=FALSE, sep = "\t")

```


Selecting only the first accession in a protein group to avoid matching the same protein group twice within the ExoCarta data.

```{r organizing_lists}
ev_human_list_ids_top1k <- ev_human_list_ids_filtered %>%
                           .[order(.$unique_experiments, decreasing = TRUE),] %>%
                           slice_head(., n = 1000)


magnet_input_first_accession <- magnet_input %>%
                                mutate(Protein.Accession.First = str_extract(Protein.Accession, "\\w+"))

# Overlap of full dataset
magnet_all_exocarta_all <- merge(magnet_input_first_accession, ev_human_list_ids_filtered)


# Overlap with just the top 1000
magnet_all_exocarta_top1000 <- merge(magnet_input_first_accession, ev_human_list_ids_top1k)


write.table(magnet_all_exocarta_top1000, paste0("output//tables//",basename,exocarta,"top1000_human_ev_proteins_magnet_all.tsv"), quote=FALSE, row.names=FALSE, sep = "\t")


magnet_all_exocarta_top100 <- (magnet_all_exocarta_top1000 %>%
                                .[order(.$unique_experiments, decreasing = TRUE),] %>%
                                slice_head(., n = 100))

```

<br/><br/>


# Figures {.tabset .tabset-fade}

## Euler Diagrams

```{r function_checkoverlap}
# Function to check overlap quantities
    check_overlap_sums <- function(original_quantity, overlap, leftover, dataset) {
      if(overlap + leftover == original_quantity) {print(paste0("CONFIRMED: ", dataset, "Quantities add up"))}
      if(overlap + leftover != original_quantity) {print(paste0("ERROR: ", dataset, "Quantities DO NOT add up - CHECK CODE/DATA"))}
    }

```


```{r counts_list_totals}
# Dataset sizes
count_magnet_total <- nrow(magnet_input)
count_exocarta_total <- nrow(ev_human_list_ids_filtered)

```

$~$

#### Top 1000 proteins in ExoCarta

```{r counts_by_list_exocarta_top1000}
# Overlapping with top 1000
count_exocarta_top1000_found_in_magnet <- nrow(magnet_all_exocarta_top1000)
count_exocarta_top1000 <- 1000
count_exocarta_top1000_leftover_exocarta <- count_exocarta_top1000 - count_exocarta_top1000_found_in_magnet
count_exocarta_top1000_leftover_magnet <- count_magnet_total - count_exocarta_top1000_found_in_magnet

    # Checking overlaps
        check_overlap_sums(original_quantity = count_magnet_total,
                           overlap = count_exocarta_top1000_found_in_magnet,
                           leftover = count_exocarta_top1000_leftover_magnet,
                               dataset = "Mag-Net (top 1000 exocarta list)")
         
        check_overlap_sums(original_quantity = count_exocarta_top1000,
                           overlap = count_exocarta_top1000_found_in_magnet,
                           leftover = count_exocarta_top1000_leftover_exocarta,
                               dataset = "Exocarta (top 1000 list)")  

# Eulerr diagram of top 1000 ExoCarta with Mag-Net
    setfit_top1000 <- euler(c(A = count_exocarta_top1000_leftover_magnet, B = count_exocarta_top1000_leftover_exocarta, "A&B" = count_exocarta_top1000_found_in_magnet))
    # setfit_top1000
    
    euler_diagram_top1000 <- plot(setfit_top1000, quantities = list(cex = 1.7), fills = list(fill = c("#5D3A9B","#E66100","gray"), alpha = 0.5), labels = list(cex = 1.7, labels = c(paste("Mag-Net"), paste("  ExoCarta\n(Top 1000)\n \n \n "), paste("Both"))))

    # Export plot as svg
    ggsave(file = paste0("output//plots//",basename,exocarta,"euler_exocarta_top1000_vs_magnet_all.svg"), plot=euler_diagram_top1000, width=7, height=5)

    
```


```{r plot_euler_top1000_print, width=7, height=5}
euler_diagram_top1000

```

$~$

#### Top 100 proteins in ExoCarta

```{r counts_by_list_exocarta_top100}
# Overlapping with top 1000
count_exocarta_top100_found_in_magnet <- nrow(magnet_all_exocarta_top100)
count_exocarta_top100 <- 100
count_exocarta_top100_leftover_exocarta <- count_exocarta_top100 - count_exocarta_top100_found_in_magnet
count_exocarta_top100_leftover_magnet <- count_magnet_total - count_exocarta_top100_found_in_magnet

    # Checking overlaps
        check_overlap_sums(original_quantity = count_magnet_total,
                           overlap = count_exocarta_top100_found_in_magnet,
                           leftover = count_exocarta_top100_leftover_magnet,
                               dataset = "Mag-Net (top 100 exocarta list)")
         
        check_overlap_sums(original_quantity = count_exocarta_top100,
                           overlap = count_exocarta_top100_found_in_magnet,
                           leftover = count_exocarta_top100_leftover_exocarta,
                               dataset = "Exocarta (top 100 list)")  

# Eulerr diagram of top 1000 ExoCarta with Mag-Net
    setfit_top100 <- euler(c(A = count_exocarta_top100_leftover_magnet, B = count_exocarta_top100_leftover_exocarta, "A&B" = count_exocarta_top100_found_in_magnet))
    # setfit_top1000
    
    euler_diagram_top100 <- plot(setfit_top100, quantities = list(cex = 1.7), fills = list(fill = c("#5D3A9B","#E66100","gray"), alpha = 0.5), labels = list(cex = 1.7, labels = c(paste("Mag-Net\n "), paste("\nExoCarta\n(Top 100)\n"), paste("Both"))))

    # Export plot as svg
    ggsave(file = paste0("output//plots//",basename,exocarta,"euler_exocarta_top100_vs_magnet_all.svg"), plot=euler_diagram_top100, width=7, height=5)

    
```


```{r plot_euler_top100_print, width=7, height=5}
euler_diagram_top100

```


<br/><br/>


## Percentages

Of the proteins that overlap between Mag-Net and ExoCarta, calculated what percent of those were enriched, depleted, or not significant in the particle-enriched samples relative to total plasma.

* **Starting with the top 1000 ExoCarta proteins:**
  - 729 found in Mag-Net
  - 75.99% are enriched
  - 6.04% are depleted
  - 17.97% are not significant

* **Starting with the top 100 ExoCarta proteins:**
  - 100 found in Mag-Net
  - 87% are enriched
  - 3% are depleted
  - 10% are not significant

$~$

```{r function_enrich_deplet_percent}
# Proteins found in Mag-Net from all of ExoCarta (Calculated above)
extract_percent_enr_dep <- function(dataframe, count_in_magnet, string_describing_list_used){
    
    subdata_enriched <- dataframe %>%
                        filter(type == "Enriched")
    
    subdata_depleted <- dataframe %>%
                        filter(type == "Depleted") 

    subdata_ns <- dataframe %>%
                  filter(type == "Not Significant") 
    
# Calculate percentages
    percent_enriched <- ((nrow(subdata_enriched) / count_in_magnet) *100)
    percent_enriched_formatted <- format(round(percent_enriched, digits = 2), nsmall = 2)
    print(paste0(percent_enriched_formatted,"% enriched in ",string_describing_list_used))

    percent_depleted <- ((nrow(subdata_depleted) / count_in_magnet) *100)
    percent_depleted_formatted <- format(round(percent_depleted, digits = 2), nsmall = 2)
    print(paste0(percent_depleted_formatted,"% depleted in ",string_describing_list_used))       
    
    percent_ns <- ((nrow(subdata_ns) / count_in_magnet) *100)
    percent_ns_formatted <- format(round(percent_ns, digits = 2), nsmall = 2)
    print(paste0(percent_ns_formatted,"% not significant in ",string_describing_list_used))  
    
    
      if(sum(percent_enriched + percent_depleted + percent_ns) == 100) {print(paste0("CONFIRMED: ",string_describing_list_used," sums to 100%"))}
      if(sum(percent_enriched + percent_depleted + percent_ns) != 100) {print(paste0("ERROR: ",string_describing_list_used," DOES NOT sum to 100% - CHECK CODE/DATA"))}
    }


```


```{r overlap_fraction_enriched}
# Proteins found in Mag-Net from top 1000 ExoCarta (Calculated above)
extract_percent_enr_dep(dataframe = magnet_all_exocarta_top1000,
                        count_in_magnet = count_exocarta_top1000_found_in_magnet,
                        string_describing_list_used = "top 1000 from ExoCarta")

# Proteins found in Mag-Net from top 100 ExoCarta (Calculated above)
extract_percent_enr_dep(dataframe = magnet_all_exocarta_top100,
                        count_in_magnet = count_exocarta_top100_found_in_magnet,
                        string_describing_list_used = "top 100 from ExoCarta")

```



$~$

<br/><br/>


## Labeled Volcano Plot

Taking the top 1000 or 100 protein hits by times observed from ExoCarta, plot a volcano plot of the -Log~10~(adjusted p-value) relative to the Log~2~(fold change) of those proteins also identified in Mag-Net and colored by their enrichment or depletion status. The top 15-most abundant proteins by the times observed in ExoCarta are labeled with their gene name and their data points re-colored.

```{r function_volcano_plots, warning = FALSE}
# Set aesthetic components of volcano plot to be generated in next section.
    # Setting legend text
        legendval <- "Protein Type"
        
    # Setting y- and x-axes
        yaxval <- expression("-Log"[10]~"(adjusted p-value)")
        xaxval <- expression("Log"[2]~"(fold change)")

    # Setting p-value cutoff marking in figure (And setting to log 10 scale)
        yaxFilter <- log(0.05, 10)
    
    # Setting depletion and enrichment value cutoff markings in figure (And setting to log 2 scale)
        xaxFilterDeplet <- log(0.5, 2)
        xaxFilterEnrich <- log(2, 2)

        
volcano_labeled <- function(dataframe, x_limits_volc, depletion_label_number, figure_height, figure_width, file_suffix){

# Code for a ggplot2 object.
volcanoplot_labeled <- ggplot(data=dataframe, aes(x=Log2FC, y=-Log10pValue, col=type, label=Protein.Accession)) + 
  
  # Add horizontal line representing significance cut-off of y = -Log10(0.05)
  geom_hline(yintercept=-yaxFilter, linetype="dashed", color = "azure4", linewidth=0.75) +
  # Add vertical lines representing depletion fold change cut-off of x = Log2(0.5), and enrichment fold change cut-off of x = Log2(2)
  geom_vline(xintercept=xaxFilterDeplet, linetype="dashed", color = "azure4", linewidth=0.75) +
  geom_vline(xintercept=xaxFilterEnrich, linetype="dashed", color = "azure4", linewidth=0.75) +
  
  # Set size and transparency of points.
  geom_point(shape=19, alpha = 1, size = 4) + 
  
  # Add labels for most abundant exocarta proteins
  geom_label_repel(data = (dataframe %>%
                           .[order(.$unique_experiments, decreasing = TRUE),] %>%
                           slice_head(., n = 15)),
                  aes(label = Gene), 
                  size = 7,
                  seed = 42,
                  max.overlaps = Inf,
                  box.padding = 0.2,
                  color = "black",
                  show.legend = FALSE) + 
  
  # Add labels for protein found in the barplots
  geom_label_repel(data = (dataframe %>%
                           filter(., type == "Depleted") %>%
                           .[order(.$unique_experiments, decreasing = TRUE),] %>%
                           slice_head(., n = depletion_label_number)),
                  aes(label = Gene), 
                  size = 7,
                  seed = 42,
                  max.overlaps = Inf,
                  box.padding = 0.2,
                  color = "black",
                  show.legend = FALSE) + 
  
  #Add point to clearly label proteins of interest.
  geom_point(data = (dataframe %>%
                     .[order(.$unique_experiments, decreasing = TRUE),] %>%
                     slice_head(., n = 15)),
                    aes(x=Log2FC, y=-Log10pValue), 
                    shape=21, alpha = 1, size = 4, color = "black", fill="cyan") + 
  
  #Add point to clearly label proteins of interest.
  geom_point(data = (dataframe %>%
                     filter(., type == "Depleted") %>%
                     .[order(.$unique_experiments, decreasing = TRUE),] %>%
                     slice_head(., n = depletion_label_number)),
                    aes(x=Log2FC, y=-Log10pValue), 
                    shape=21, alpha = 1, size = 4, color = "black", fill="salmon") + 
    
  # Setting x-axis limits
  scale_x_continuous(limits = x_limits_volc, expand = c(0, 0)) +
  # Set minimal theme
  theme_classic()+
  # Remove major and minor grid lines, alter text and legend formatting.
  theme(plot.margin=grid::unit(c(t = 0.2,  r = 0.4, b = 0, l = 0), "in"),  #0.1,0.4,0,0), "in"), # t, r, b, l 
        axis.line.x.bottom = element_line(linewidth=2),
        axis.line.y.left = element_line(linewidth=2),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title=element_text(size=24),
        axis.text.x = element_text(size=24, color = "black"),
        axis.text.y = element_text(size=24, color = "black"),
        legend.position="none")+

  # Add y-axis label and x-axis label
  ylab(yaxval) +
  xlab(xaxval) +

  # Manually set color scale by category
  scale_color_manual(values=c("Enriched"="blue", "Depleted"="red2", "Not Significant"="grey40"))

# Export plot as svg
ggsave(file = paste0("output//plots//",basename,exocarta,file_suffix,".svg"), plot=volcanoplot_labeled, width=figure_width, height=figure_height)

volcanoplot_labeled

}


```

```{r plot_volcano_plots, warning = FALSE, fig.show='hide'}
# Setting scale for volcano plots
    ratio <- 3.1/2.07
    height_volc <- 8
    width_volc <- height_volc*ratio

# Remove comment to look at only the top 100 proteins
    volcano_top1000exo  <-  volcano_labeled(dataframe = magnet_all_exocarta_top1000, 
                                            x_limits_volc = c(-10,10), 
                                            depletion_label_number = 5,
                                            figure_height = height_volc, 
                                            figure_width= width_volc, 
                                            file_suffix ="volcano_magnet_all_exocarta_top1000_human_ev_labeled")


# Only the top 100 proteins in ExoCarta
    volcano_top100exo  <-  volcano_labeled(dataframe = magnet_all_exocarta_top100,
                                           x_limits_volc = c(-10,10),
                                           depletion_label_number = 3,
                                           figure_height = height_volc,
                                           figure_width= width_volc,
                                           file_suffix ="volcano_magnet_all_exocarta_top100_human_ev_labeled")
```

$~$

#### Top 1000 proteins in ExoCarta

* Two data points that did not reach statistical significance with FCs greater than 13 were omitted from the volcano plot to improve visualization of the other data points and top ExoCarta protein labels. 

```{r plot_volcano_top1000_print, warning = FALSE, width = width_volc, height = height_volc}

volcano_top1000exo

```

$~$

#### Top 100 proteins in ExoCarta

```{r plot_volcano_top100_print, warning = FALSE, width = width_volc, height = height_volc}

volcano_top100exo
```

$~$

<br/><br/>

## Histogram

Taking the top 1000 protein hits by times observed from ExoCarta, plot a histogram of the counts of those proteins also identified in Mag-Net and colored by their enrichment or depletion status.


```{r function_histogram, warning = FALSE, fig.show='hide'}
plot_histogram <- function(dataframe, bin_width, x_limits_hist, figure_height, figure_width, file_suffix){

histogram_plot<- (ggplot(dataframe, aes(x=Log2FC, color=type, fill = type)) + 
                          geom_histogram(binwidth=bin_width, alpha=0.5, position = "identity") +
                          theme_minimal()+
                          # Remove major and minor grid lines, alter text and legend formatting.
                          theme(plot.margin=grid::unit(c(t = 0.25,  r = 0.25, b = 0, l = 0), "in"), #  0,0,0,0), "in"),
                                axis.line.x.bottom = element_blank(),
                                axis.line.y.left = element_line(linewidth=2),
                                panel.grid.major.x = element_blank(),
                                panel.grid.major.y = element_blank(),
                                panel.grid.minor.x = element_blank(),
                                panel.grid.minor.y = element_blank(),
                                axis.title = element_text(size=24),
                                axis.text.x = element_text(size=22, color = "black"),
                                axis.text.y = element_text(size=22, color = "black"),
                                legend.position="none")+
                          geom_hline(yintercept=0, linetype="solid", color = "black", linewidth=2) +
                          geom_vline(xintercept=xaxFilterDeplet, linetype="dashed", color = "azure4", linewidth=0.6) +
                          geom_vline(xintercept=xaxFilterEnrich, linetype="dashed", color = "azure4", linewidth=0.6) +
                          ylab("Count") +
                          scale_x_continuous(limits = x_limits_hist, expand = c(0, 0)) +
                          scale_fill_manual(values=c("Enriched"="blue", "Depleted"="red2", "Not Significant"="grey40")) +
                          scale_color_manual(values=c("Enriched"="blue", "Depleted"="red2", "Not Significant"="grey40")))

ggsave(file = paste("output//plots//",basename,exocarta,"histogram_",file_suffix,".svg", sep = ""), plot=histogram_plot, width=figure_width, height=figure_height)

histogram_plot

}


```



```{r plot_histogram, warning = FALSE, fig.show='hide'}
        xaxFilterDeplet <- log(0.5, 2)
        xaxFilterEnrich <- log(2, 2)

# Setting enrichment/depletion type as factor.
        magnet_all_exocarta_top1000_histfactor <- magnet_all_exocarta_top1000
        magnet_all_exocarta_top1000_histfactor$type <- factor(magnet_all_exocarta_top1000_histfactor$type, levels=c("Depleted", "Enriched", "Not Significant"))
        # levels(magnet_all_exocarta_top1000_histfactor$type)
        
        magnet_all_exocarta_top100_histfactor <- magnet_all_exocarta_top100
        magnet_all_exocarta_top100_histfactor$type <- factor(magnet_all_exocarta_top100_histfactor$type, levels=c("Depleted", "Enriched", "Not Significant"))
        # levels(magnet_all_exocarta_top100_histfactor$type)

        
# Setting plot dimenstions        
height_hist <- (height_volc-3)
width_hist <- width_volc


histogram_top1000exo  <-  plot_histogram(dataframe = magnet_all_exocarta_top1000_histfactor,
                                  bin_width = 0.5,
                                  x_limits_hist = c(-10,10),
                                  figure_height = height_hist, 
                                  figure_width = width_hist,                                   
                                  file_suffix = "magnet_all_exocarta_top1000_human_ev")

histogram_top100exo  <-  plot_histogram(dataframe = magnet_all_exocarta_top100_histfactor,
                                  bin_width = 0.5,
                                  x_limits_hist = c(-10,10),
                                  figure_height = height_hist, 
                                  figure_width = width_hist, 
                                  file_suffix = "magnet_all_exocarta_top100_human_ev")

```

$~$

#### Top 1000 proteins in ExoCarta

* Two data points that did not reach statistical significance with FCs greater than 10 were omitted from the volcano plot to improve visualization of the other data points and top ExoCarta protein labels. 

```{r plot_histogram_top1000_print, warning = FALSE, width = width_hist, height = height_hist}

histogram_top1000exo

```

$~$

#### Top 100 proteins in ExoCarta

```{r plot_histogram_top100_print, warning = FALSE, width = width_hist, height = height_hist}

histogram_top100exo

```

<br/><br/>

## Figure S3

```{r plot_supplementary_figure_s, warning = FALSE, fig.show='hide'}


supp_height <- height_volc + height_hist
supp_width <- width_volc + width_hist

supp_height_ratio <- height_hist/supp_height

supplementary_figure <- (histogram_top1000exo + histogram_top100exo + volcano_top1000exo + volcano_top100exo + plot_layout(heights = c(supp_height_ratio,(1-supp_height_ratio))) + plot_annotation(tag_levels = 'a') & theme(plot.tag = element_text(size = 45, face = "bold")))


ggsave(file = paste("output//plots//",basename,exocarta,"Supplementary_Figure_2.svg", sep = ""), plot=supplementary_figure, width=supp_width, height=supp_height)

```


```{r plot_supplementary_figure_s_print, warning = FALSE, width = supp_width, height = supp_height}

supplementary_figure

```

<br/><br/>
